Plant functional type effects on biomass partitioning

### 2014-12-08 manuscript/draftpaper.Rnw
Minor figure formatting and captions

<<results='asis'>>=
print(xtable(g0, label="table/gamr2table",
      caption="Explained variance by plant functional type (PFT), plant height (H), moisture index (MI) and growing season average temperature (mgdd0), for six whole-plant variables."),
      include.rownames=FALSE, caption.placement="top")
@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure1.pdf}
    \caption{(a) Global coverage of the climate space by the dataset. Hexagons are terrestrial observations extracted from Worldclim \cite{worldclim} (colored by number of 0.5\degree~cells, cut off at 6000mm MAP), excluding areas without woody vegetation (taken from the global land cover database GLC-SHARE \cite{lathamglobal}) Triangles are averages for the three PFTs across all contributed studies. (b) Leaf mass fraction (leaf mass / aboveground biomass) by plant functional type. Each symbol is an individual plant. Lines are generalized additive model fits. (c) and (d) Leaf mass fraction (LMF) and leaf area ratio (LAR) at the average plant height in the dataset, estimated from panel (b). Error bars are 95\% confidence intervals. Letters denote significant differences.}
    \label{fig:figure1}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{Figure2.pdf}
    \caption{Average leaf mass per unit basal stem area (panel 1), and leaf area per unit basal stem area (panel 2) for the three major plant functional types. Error bars are 95\% confidence interval for the mean (calculated with a mixed-effects model with species within study as the random effect). Letters denote significant differences (at $\alpha = 0.05$). }
    \label{fig:figure2}
\end{figure}

>>>>

<<results='asis'>>=
print(xtable(g0, label="table/gamr2table",
      caption="Explained variance by plant functional type (PFT), plant height (H), moisture index (MI) and growing season average temperature (mgdd0), for six whole-plant variables. Each variable was added as a smooth term in a generalized additive model, with the exception of PFT (a categorical variable)."),
      include.rownames=FALSE, caption.placement="top")
@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{Figure1.pdf}
    \caption{(a) Global coverage of the climate space by the dataset. Hexagons are terrestrial observations, excluding areas without woody vegetation, colored by number of 0.5\degree~cells, cut off at 6000mm MAP. Triangles are averages for the three PFTs across all contributed studies. (b) Leaf mass fraction (LMF = leaf mass / aboveground biomass) by PFT. Each symbol is an individual plant. Lines are generalized additive model fits. (c) and (d) Leaf mass fraction (LMF) and leaf area ratio (LAR) at the average plant height in the dataset, estimated from panel (b). Error bars are 95\% confidence intervals. Letters denote significant differences.}
    \label{fig:figure1}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{Figure2.pdf}
    \caption{Average leaf mass per unit basal stem area (panel 1), and leaf area per unit basal stem area (panel 2) for the three major PFTs. Error bars are 95\% confidence interval for the mean (calculated with a mixed-effects model with species within study as the random effect). Letters denote significant differences (at $\alpha = 0.05$). }
    \label{fig:figure2}
\end{figure}
